Constraints on the quasi-normal mode frequencies of the LIGO-Virgo signals by making full use of gravitational-wave modeling

### 2021-02-03 papers/intro_paper/acknowledgements.tex
updated appendix
cite some early QNM papers and reviews

LIGO Clusters. \comment{AB: Our cluster!!!}
R.B. acknowledges financial support from the European Union's Horizon 2020 research and innovation programme under the Marie Sk\l odowska-Curie grant agreement No. 792862. This research was supported by the Amaldi Research Center funded by the MIUR program ``Dipartimento di Eccellenza'' (CUP:~B81I18001170001).

>>>>

The authors would like to thank everyone at the frontline of the Covid-19 pandemic. We would like to acknowledge the computing resources at the AEI and the LIGO Scientific Collaboration, specifically the Hypatia and CIT clusters. R.B. acknowledges financial support from the European Union's Horizon 2020 research and innovation programme under the Marie Sk\l odowska-Curie grant agreement No. 792862, the European Union's H2020 ERC, Starting Grant agreement no.~DarkGRA--757480, and from the MIUR PRIN and FARE programmes (GW-NEXT, CUP:~B84I20000100001). We also acknowledge support from the Amaldi Research Center funded by the MIUR program ``Dipartimento di Eccellenza'' (CUP:~B81I18001170001).

### 2021-02-03 papers/intro_paper/intro.tex
cite some early QNM papers and reviews

The observation of GWs has had significant astrophysical and cosmological
implications~\cite{TheLIGOScientific:2016htt,GBM:2017lvd,Monitor:2017mdv,Abbott:2017xzu}. It
has also allowed us to probe fundamental
physics and test predictions of Einstein's theory of General Relativity
(GR) in the previously unexplored highly-dynamical, and strong field
regime~\cite{TheLIGOScientific:2016src,Abbott:2018lct,LIGOScientific:2019fpa}. In GR, a binary black hole (BBH) system is described by
three distinct phases: an early \textit{inspiral}, where the two
compact objects spiral in loosing energy because of the emission of GWs, a \textit{merger} marked by the
formation of a common apparent horizon, and a \textit{ringdown}, during which the newly formed remnant object settles down to a Kerr BH emitting quasi-normal-modes (QNMs)~\cite{Vishveshwara:1970cc}\abhi{cite some of the other early QNM papers} (i.e., damped oscillations with specific, discrete frequencies and decay times).

>>>>

The observation of GWs has had significant astrophysical and cosmological
implications~\cite{TheLIGOScientific:2016htt,GBM:2017lvd,Monitor:2017mdv,Abbott:2017xzu}. It
has also allowed us to probe fundamental
physics and test predictions of Einstein's theory of General Relativity
(GR) in the previously unexplored highly-dynamical, and strong field
regime~\cite{TheLIGOScientific:2016src,Abbott:2018lct,LIGOScientific:2019fpa}. In GR, a binary black hole (BBH) system is described by
three distinct phases: an early \textit{inspiral}, where the two
compact objects spiral in loosing energy because of the emission of GWs, a \textit{merger} marked by the
formation of a common apparent horizon, and a \textit{ringdown}, during which the newly formed remnant object settles down to a Kerr BH emitting quasi-normal-modes (QNMs)~\cite{Vishveshwara:1970zz,Vishveshwara:1970cc,Teukolsky:1973ha,Press:1973zz,Chandrasekhar:1975zza,Detweiler:1980gk,Kokkotas:1999bd,Berti:2009kk}\abhi{cite some of the other early QNM papers} (i.e., damped oscillations with specific, discrete frequencies and decay times).
